Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-05-11 code/paper.Rmd
stash
trying to do topic modelling

@@

@@

>>>>

# the talk pages for all WH sites, with WP pages (n = 846)
wh_wiki_talk_pages <-  readRDS(here::here("data", 
                     "wh_wiki_table_talk_page_content.rds"))

@@

Which articles have the most reverts?

@@

tidy_talk <- 
enframe(unlist(wh_wiki_talk_pages)) %>% 
  mutate(clean_text = str_remove_all(value, "\n|\t")) %>% 
  unnest_tokens(word, clean_text) %>% 
  anti_join(stop_words) %>% 
  filter(!word %in% c("article", "page", "talk", "utc", "class", "edit", "project's"))

# top words
tidy_talk %>% 
  count(word, sort = TRUE)

# biggest documents
tidy_talk %>% 
  group_by(name) %>% 
  tally(sort = TRUE)
```

The statistic tf-idf identifies words that are important to a document in a collection of documents; in this case, we’ll see which words are important in one of the talk pages compared to the others.

```{r eval = FALSE}

library(drlib) # devtools::install_github("dgrtwo/drlib")

tidy_talk_tf_idf <- tidy_talk %>%
  count(name, word, sort = TRUE) %>%
  bind_tf_idf(word, name, n) %>%
  arrange(-tf_idf) %>%
  group_by(name) %>%
  top_n(10) %>%
  ungroup

tidy_talk_tf_idf %>%
  mutate(word = reorder_within(word, tf_idf, name)) %>%
  ggplot(aes(word, tf_idf, fill = name)) +
  geom_col(alpha = 0.8, show.legend = FALSE) +
  facet_wrap(~ name, scales = "free", ncol = 3) +
  scale_x_reordered() +
  coord_flip() +
  theme(strip.text=element_text(size=11)) +
  labs(x = NULL, y = "tf-idf",
       title = "Highest tf-idf words in talk pages ",
       subtitle = "")
```
